---
title: "HW2"
author: "Thomas Kwok"
date: "March 7, 2019"
output: word_document
---

1a. 

```{r}
library(survival)
#install.packages("survminer")
library(survminer)
#install.packages("sas7bdat")
library(sas7bdat)
setwd("C:/Users/thoma/Desktop/Spring 2019/Survival Analysis")
vets <- read.sas7bdat('vets.sas7bdat')
q1 <- survfit(Surv(SURVT)~CT1, data=vets)
plot(q1, lty = 2:3, xlab = "Survival Time", ylab = "CT1")
legend(600, 1, legend=c("Other", "Large Cell"), lty = 1:2)
largecell <- survdiff((Surv(SURVT)~CT1==1), data=vets)
largecell
```

According to the graph, it seems that that the Large Cell survive longer than the Other group. Though one thing to keep in mind as shown on the log-rank test is that there are a lot more observed for the Other than there is for the Large Group. Also the p value for the log-rank test shows there is some significance in the data as it is lower than alpha of 0.5.

2a.

```{r}
addicts <- read.sas7bdat('addicts.sas7bdat')
q2 <- survfit(Surv(SURVT)~CLINIC, data=addicts)
plot(q2, lty = 2:3, xlab = "Survival Time", ylab = "Clinic")
legend(600, 1, legend=c("Clinic 1", "Clinic 2"), lty = 1:2)
```

My data shows that the survival time for the patients in Clinic 2 is often better than the survival time for the patients in Clinic 1. 

2b. The p-value for the log-rank and Wilcoxon test both are less than alpha 0.05 so it shows that both reject the null hypothesis and the clinics are significantly different. The chi-square for the Log-Rank is higher than the log-rank for Wilcoxon so that means that the data is spread out instead of having more emphasis on the first few data.


2c.
```{r}
addicts$DOSE[which(addicts$DOSE >= 70)] = 'high'
addicts$DOSE[which(addicts$DOSE < 55)] = 'low'
addicts$DOSE[which(addicts$DOSE %in% c(55, 60, 65))] = 'medium'
q3 <- survfit(Surv(SURVT)~DOSE, data=addicts)
plot(q3, lty = 2:5, xlab = "Survival Time", ylab = "Methadone dose")
legend(600, 1, legend=c("Low", "Medium", "High"), lty = 2:5)
```

The KM curves indicate taht people with higher doses will have the best survival prognosis while low seems to be a bit better than medium. 